title

### 2016-05-13 paper.tex
paper: notes
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Cloud providers are increasingly reliant upon extensions to distributed
storage system such as Ceph as is shown in Figure~\ref{fig:objclass-dev}
by a marked increase in production Ceph extensions. The construction of
extensions is not limited to core developers; the community has been receptive
to contributions with the recent inclusion by CERN developers of an extension
for performing limited numeric operations on object data~\cite{cls_numops}.

>>>>

Cloud providers are increasingly reliant upon extensions to distributed
storage system such as Ceph as is shown in Figure~\ref{fig:objclass-dev}
by a marked increase in production Ceph extensions.

Figure~\ref{fig:objclass-dev} also shows the number of lines of C++
code written to create these extensions.

The construction of extensions is not limited to core developers; the
community has been receptive to contributions with the recent inclusion by
CERN developers of an extension for performing limited numeric operations on
object data~\cite{cls_numops}, and a mechanism for dynamically defining
extensions using Lua~\cite{cls_lua}.

Operating systems and containers are similar. AUFS, dockerfile

\section{Recurring Problem}

Describe CORFU briefly, and then show the physical design challenge. The
performance decision changes depending on the mix of hardware and software
versions and configurations.
